---
title: "Homework 4"
author: "Namson Ngo-Le"
date: "November 14, 2018"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(reshape2)
```

```{r 3}
lum <- read_csv("../data/final/tun_lum_governorate_93_13_tidy.csv")

# Plot of Luminosity by Governorate by Year
ggplot(lum, aes(x = year, y = mean, colour=NAME_1)) +
geom_line() +
xlab("Year") +
ylab("Luminosity") +
ggtitle("Luminosity by Governorate by Year") + labs(color='Governorate') 

# Subset of Data
ggplot(subset(lum, NAME_1 %in% c("Tunis", "Sfax", "Monastir", "Tataouine")),
       aes(x=year,
       y=mean,
       color=NAME_1, group = NAME_1))+
  geom_line() +
ylab("Luminosity") +
ggtitle("Luminosity of Four Governorates by Year") + labs(color='Governorate') 

tun <- lum %>% 
   group_by(year) %>%                         
   summarise(count = sum(count), sum = sum(sum))
   
tunisia_economy <- read_csv("../data/intermediate/tunisia_economy.csv")
tunisia <- merge(tun,tunisia_economy,by="year")

tunisia$avg_lum <- tunisia$sum / tunisia$count

melt_tunisia <- melt(tunisia,id="year")

melt_tunisia <- melt_tunisia %>%
      group_by(variable) %>%
      arrange(year) %>%
      mutate(indexedvalue = 100 * value / first(value))

ggplot(subset(melt_tunisia, variable %in% c("avg_lum", "govt_debt", "gdp_per_capita", "gdp_growth", "inflation", "unemployment_rate")),
       aes(x=year,
       y=indexedvalue,
       color=variable, group = variable))+
  geom_line() + ggtitle("Indexed Economic Indicators for Tunisia 1992-2013") +xlab("Year") + ylab("Indexed Value") + labs(color='Variable') 
  
cor_tunisia <- cor(tunisia)
cor_tunisia

    ggplot(data = tunisia, mapping = aes(x = year)) + 
  geom_line(aes(y = avg_lum), color = "blue", size = 1.5, alpha = .5) + 
  geom_line(aes(y = gdp_ppp), color = "yellow", size = 1.5, alpha = .5) +
              theme(legend.position=c(.1,.85))			  


    ggplot(data = tunisia, mapping = aes(x = year)) + 
  geom_line(aes(y = avg_lum), color = "blue", size = 1.5, alpha = .5) + 
  geom_line(aes(y = gdp_growth), color = "green", size = 1.5, alpha = .5) +
              theme(legend.position=c(.1,.85))		         
              
    ggplot(data = tunisia, mapping = aes(x = year)) + 
  geom_line(aes(y = avg_lum), color = "blue", size = 1.5, alpha = .5) + 
  geom_line(aes(y = govt_debt), color = "red", size = 1.5, alpha = .5) +
              theme(legend.position=c(.1,.85))		