---
title: "Mariem_exploratory"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Question 3

My team project evolves around exploring data about Tunisia. 
Note: the term "Governorate" refers to the 24 *Counties* that devide the country.
```{r}
library(ggplot2)
library(tidyverse)
library(reshape)
```

While the focus in this question will be the 'unemployment' variable, let us first explore our dataset.

```{r}
population_unemployed <- readxl::read_excel('../data/intermediate/hw4-mariem/Number of unemployed people from the population aged 15 years and over in 2014.xlsx')
tbl_df(population_unemployed)
```

Let us have a closer look at the *unemployment* data (by number of individuals).
```{r}
skimr::skim(population_unemployed)
```

Let us also have a closer look at the *population* data.
Note: total population will be used to calculate percent unemployment.

```{r}
population_all <- readxl::read_excel('../data/intermediate/hw4-mariem/Number of population aged 15 years and over in 2014.xlsx')
tbl_df(population_all)
```

```{r}
skimr::skim(population_all)
```

```{r}
tidy_unemploy <- gather(select(population_unemployed,Male, Female, Governorate ), key, value, -Governorate)
tbl_df(tidy_unemploy)
```

We will start with a simple bar plot to get a sense of population size by gender.
```{r}
tidy_total_pop <- gather(select(population_all,Male, Female, Governorate ), key, value, -Governorate)
tbl_df(tidy_total_pop)
```

```{r}
pop_gender <- tidy_total_pop %>% group_by(key) %>% summarize(population = sum(value))
tbl_df(pop_gender)
```

### Graph 1

```{r}
ggplot(pop_gender, aes(x = key, y = population)) +
  geom_bar(stat = "identity") +
  ggtitle("Total population by gender")
```

As of 2014, there are more females than males in Tunisia (all governorates included). Nevertheless, it is worth noting that the difference is not extreme. Both the Female and Male population is around 4 million.

### Graph 2-a

What about unemployment?

```{r}
unemploy_gender <- tidy_unemploy %>% group_by(key) %>% summarize(unemployment = sum(value))
tbl_df(unemploy_gender)
```

```{r}
ggplot(unemploy_gender, aes(x = key, y = unemployment)) +
  geom_bar(stat = "identity") +
  ggtitle("Number of unemployed citizens by gender")
```

This is quite interesting information. While there are more *female* citizens in Tunisia, unemployment seems higher for *males*. But, the above graph is showing the sum of unemployed *individuals* as opposed to *percent* unemployment. We should therefore combine both data (total population & unemployment.)

```{r}
combo_pop_unemploy <- merge(tidy_unemploy ,tidy_total_pop,by=c("Governorate","key"))
colnames(combo_pop_unemploy)[2] <- "gender"
colnames(combo_pop_unemploy)[3] <- "unemployment"
colnames(combo_pop_unemploy)[4] <- "population"
combo_pop_unemploy_gender_perct_all <- combo_pop_unemploy %>% group_by(gender) %>% mutate(perc_unemploy = 100 * ((unemployment) / (population)))

tbl_df(combo_pop_unemploy_gender_perct_all)
```

### Graph 2-b

```{r}
perct_u_byGender <- merge(unemploy_gender,pop_gender,by=c("key")) %>% mutate(perc_unemploy = 100 * ((unemployment) / (population))) %>% select(key, perc_unemploy)

ggplot(perct_u_byGender, aes(x = key, y = perc_unemploy)) +
  geom_bar(stat = "identity") +
  ggtitle("Percent unemployed citizens by gender")
```

The bar chart above confirms (even more clearly) that it is indeed the case that Female unemployment (as a percentage this time) is lower than that of men *at the country level*.

### Graph 3

Does that pattern persist throughout the different governorates?

```{r, echo = FALSE}
governorate_gender_perct_unemploy_e <- readxl::read_excel('../data/intermediate/hw4-mariem/governorate_gender_perct_unemploy.xlsx')
```

```{r}
tbl_df(governorate_gender_perct_unemploy_e)
```

```{r}
theme_dotplot <-theme_bw(14) +
  theme(axis.text.y =element_text(size =rel(.75)),
        axis.ticks.y =element_blank(),
        axis.title.x =element_text(size =rel(.75)),
        panel.grid.major.x =element_blank(),
        panel.grid.major.y =element_line(size = 0.5),
        panel.grid.minor.x =element_blank())


ttidy <-  governorate_gender_perct_unemploy_e %>%
  select(Governorate, female_perct_u, male_perct_u) %>%
  gather(key = variable, value = percent,-Governorate) %>%
  mutate(variable= factor(variable, levels =c("male_perct_u", "female_perct_u")))

ggplot(ttidy,aes(percent,fct_reorder2(Governorate, variable,-percent),color = variable))+
  geom_point() + ylab("")+
  theme_dotplot +
  theme(legend.position = "top",legend.title =element_blank())
```

Yes.
While the population of females is larger than that of man, the above graph does confirm the fact that for the vast majority of Governorates the female percent unemployment is lower than male's percent unemployment. Additionally, this graph shows that for the Governorates of Kebili, Manouba and Medenine, the pattern is reversed. That is an interesting fact worth investigating. An initial assumption is that those Governorates rely more heavily on farming and that may (or may not be) an occupation more acceessible to men. 
It is also worth noting that the capital (which encompasses the Governorates of Tunis and Ariana) neither has the lowest nor the highest percent unemployment (both for males and females)



### PART II

```{r}
lumData <- read_csv("../data/final/tun_lum_governorate_93_13_tidy.csv")
lumData$Gov_longName <- lumData$NAME_1
lumData$Gov_longName <- sub("^", "Governorate of ", lumData$Gov_longName)
lumData$Gov_longName <- ifelse(lumData$NAME_1 == "Kebili", "Governorate of Kebili", 
                               ifelse(,)
                               ,"NA")
tbl_df(lumData)

```

```{r}
lumData2013 <- lumData[lumData$year == "2013",]
tbl_df(lumData2013)
lumData2013$NAME_1
```

```{r}
tbl_df(lumData2013)
```
### Comment:
Sfax is the 2nd city from an economic stand point in Tunisia. It is surprising that it ranks relatively low for luminosity.
Let us have a closer look:
[insert Namsom luminosity mean Vs population sctatter plot]
If we had all the pixel values we could consider plotting a box plot to get a better sense of variance within a governorate.

```{r fig.height=5, fig.width=5}
g <- ggplot(lumData2013, aes(x = mean, y = fct_reorder(NAME_1, mean))) +
    geom_point(color = "blue") + ylab("") +
    ggtitle("Luminosity per Governovates in 2013 (mean)")
g

g <- ggplot(lumData2013, aes(x = lumData2013$media, y = fct_reorder(NAME_1, lumData2013$media))) +
    geom_point(color = "blue") + ylab("") +
    ggtitle("Luminosity per Governovates in 2013 (median)")
g
```


```{r fig.height=5, fig.width=5}
g <- ggplot(lumData2013, aes(x = lumData2013$media, y = fct_reorder(NAME_1, lumData2013$media))) +
    geom_point(color = "blue") + ylab("") +
    ggtitle("Luminosity per Governovates in 2013 (median)")
g
```

### Comment:
Sfax is the 2nd city from an economic stand point in Tunisia. It is surprising that it ranks relatively low for luminosity.
Let us have a closer look:
[insert Namsom luminosity mean Vs population sctatter plot]
If we had all the pixel values we could consider plotting a box plot to get a better sense of variance within a governorate.
TODO: since we do not have that data, our chosen alternative is to extract the delegeations that fall under the sfax governorate (and other) and create a boxplot where each dot repersents the mean fo a delegations



```{r}
governorate_gender_perct_unemploy_e$Governorate
```

```{r}
tbl_df(lumData)
```


```{r}
exitDF <- 
  readxl::read_excel("../data/linkage/Distribution of immigrants and emigrants by reason of exit between 2009 and 2014 11_18_2018 02_41_54.xlsx")

names(exitDF) <- exitDF[1,] #copy 1st row
exitDF <- exitDF[-1,] #remove 1st row from df
colnames(exitDF)[1] <- "Governorate"
```

```{r}
#Only keep our 3 columns of interest 
exitDF <- exitDF[,c(1,2,3,6)]
names(exitDF)[2]<-"immigrant"
names(exitDF)[3]<-"emigrant"
names(exitDF)[4]<-"emigrant_betterLife"
#as.numeric(as.character(exitDF$immigrant))
exitDF$immigrant <- as.numeric(exitDF$immigrant)
exitDF$emigrant <- as.numeric(exitDF$emigrant)
exitDF$emigrant_betterLife <- as.numeric(exitDF$emigrant_betterLife)
tbl_df(exitDF)
```

```{r fig.height=5, fig.width=5}
exitDF_nototal <- exitDF[-1,]
g <- ggplot(exitDF_nototal, aes(x = exitDF_nototal$immigrant, y = fct_reorder(Governorate, immigrant))) +
    geom_point(color = "blue") + ylab("") +
    ggtitle("Number of Immigrants coming to Tunisia between 2009 and 2014 (by Governorate)")
g
```

### Comments:
Note that we would need to divide the # of immigrants for each governorate by its specific population in order to have a normalized and more fair way to compare the different governorates to one another.
Assuming data #s is in thousands - we have suspicion that the survey is not very accurate


```{r fig.height=5, fig.width=5}
g <- ggplot(exitDF_nototal, aes(x = exitDF_nototal$emigrant, y = fct_reorder(Governorate, emigrant))) +
    geom_point(color = "blue") + ylab("") +
    ggtitle("Number of Emigrants leaving Tunisia between 2009 and 2014 (by Governorate)")
g
```

```{r fig.height=5, fig.width=5}
g <- ggplot(exitDF_nototal, aes(x = exitDF_nototal$emigrant_betterLife, y = fct_reorder(Governorate, emigrant_betterLife))) +
    geom_point(color = "blue") + ylab("") +
    ggtitle("Number of Emigrants coming or going out of Tunisia for acquisition of housing or better living conditions (by Governorate)")
g
```

## Economic Indicators of the Population in 2014 

```{r}
econDF <- 
  readxl::read_excel("../data/linkage/Economic Characteristics of the Population in 2014 11_18_2018 02_42_05.xlsx")

names(econDF) <- econDF[1,] #copy 1st row
econDF <- econDF[-1,] #remove 1st row from df
#colnames(exitDF)[1] <- "Governorate"
```

## Households by sources of energy and their use

```{r}
hhEnergy <- 
  readxl::read_excel("../data/linkage/Households by sources of energy and their use 11_18_2018 02_51_26.xlsx")

names(hhEnergy) <- hhEnergy[1,] #copy 1st row
hhEnergy <- hhEnergy[-1,] #remove 1st row from df
#colnames(exitDF)[1] <- "Governorate"

#REMOVE MOD 2 AND MOD 3 COLUMNS
```


```{r}
lum_del <- read_csv("../data/intermediate/tun_lum_delegation_93_13.csv")
tbl_df(lum_del)
```

```{r}
#del_sfax <- lum_del %>% select(lum_del,)

del_sfax <- filter(lum_del,lum_del$NAME_1 == "Sfax")
tbl_df(del_sfax)
```

```{r}
ggplot(del_sfax, aes(del_sfax$NAME_2, del_sfax$`1992_mean`)) +
  geom_boxplot() +
  geom_jitter(alpha = 0.2, width = 0.1, color = "#926d25") +
  coord_flip() +labs(y = "Luminosity (mean)", x = "Sfax delegation") +
  ggtitle("What is wrong with Sfax?",
          subtitle = "A closer look at luminosity by delegations within Sfax") +
  theme(plot.title = element_text(face = "bold")) +
  theme(plot.subtitle = element_text(face = "bold", color = "grey35"))
                     
```


### Testing branch 
```{r}
library(tidyverse)
library(choroplethr)

# data frame must contain "region" and "value" columns

df_illiteracy <- state.x77 %>% as.data.frame() %>% 
  rownames_to_column("state") %>% 
  transmute(region = tolower(`state`), value = Illiteracy)

state_choropleth(df_illiteracy,
                 title = "State Illiteracy Rates, 1977",
                 legend = "Percent Illiterate")
```

```{r}
library(statebins)
df_illit <- state.x77 %>% as.data.frame() %>% 
  rownames_to_column("state") %>% 
  select(state, Illiteracy)

# Note: direction = 1 switches the order of the fill scale 
# so darker shades represent higher illiteracy rates
# (The default is -1).

statebins(df_illit, value_col="Illiteracy",
          name = "%", direction = 1) +
  ggtitle("State Illiteracy Rates, 1977") +
  theme_statebins()
```

